Citeopotamus

### 2012-12-08 paper/paper.tex
results and some paper

@@

\begin{table}[H]
\centering
\begin{tabular} { l | c | r }
\hline\hline
        {\bf $\sum_{i = 1}^{n} RF(p_{i})$} & {\bf $\sum_{i = 1}^{n} RT(p_{i})$} & {\bf Accuracy} \\[0.5ex]
\hline
        ? & ? & ? \\[0.5ex]
\end{tabular}
\caption{Results}
\label{tab:results}
\end{table}

@@

\section{Conclusion}\label{sec:conclusion}
We have found that automatic citation placement is a difficult, but doable problem.

>>>>

\subsection{Incorrect References}
Sometimes their is an error in scraping which causes a reference to take on the incorrect number.
To prevent these refernces from polluting our data, we check for them at during parsing.
We parse the refernce section of the paper and look at every reference. If the reference does not contain all of the author names with
more than three letters, then we drop the reference and assume it is incorrect.
If there are no references left after all the references have been parsed, then the entire paper is droped.
Of our original 102O papers, 720 made it pass this phase.

@@

\begin{table}[H]
\centering
\begin{tabular} { l | c | c | r }
\hline\hline
        {\bf Reference Material} & {\bf $\sum_{i = 1}^{n} RF(p_{i})$} & {\bf $\sum_{i = 1}^{n} RT(p_{i})$} & {\bf Accuracy} \\[0.5ex]
\hline
        Abstract and Reference & 3146 & 11840 & 0.2657 \\[0.5ex]
\hline
        Abstract Only & 2642 & 11840 & 0.2231 \\[0.5ex]
\hline
        Reference Only & 1576 & 11840 & 0.1331 \\[0.5ex]
\end{tabular}
\caption{Results}
\label{tab:results}
\end{table}

@@

\section{Conclusion}\label{sec:conclusion}
We have found that automatic citation placement is a difficult, but doable problem.
Even with only the information that appears on the page, we were able to achieve over 10\% accuracy.
